ABCD Model

### 2023-11-16 ABCDModel.Rmd
Updated ABCD model prediction script with new model name.

Test Model
```{r}
abcd_brainage_model <- readRDS(here("UpdatedModels", "abcd_fit_workflow.rds"))
```

Predict Brain Age (baseline)
```{r}
brain_age_df_baseline <-
  abcd_brainage_model %>%
  predict(new_data = analysis_sample_baseline) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = analysis_sample_baseline$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

>>>>

Test Model
```{r}
abcd_brainage_model <- readRDS(here("UpdatedModels", "abcd_fit_workflow.rds"))
abcd_brainage_model <- readRDS("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/abcd_fit_workflow.Rds")

load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/abcd_fit_workflow.Rds")
```

Predict Brain Age (baseline)
```{r}
brain_age_df_baseline <-
  fit_workflow %>%
  predict(new_data = analysis_sample_baseline) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = analysis_sample_baseline$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
